\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in, right=1in, top=0.8in, bottom=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
  {\large\bfseries\color{blue!80!black}}{}{0pt}{}[\titlerule]
\begin{document}

\begin{center}
{\Huge \textbf{\textcolor{blue!80!black}{Alex Johnson}}} \\[3pt]
    28 years old, Single, British \\
    London, UK \\[5pt]
    {\faPhone*} +44 (20) 7946-0958 \quad
    {\faEnvelope} \href{mailto:alex.johnson@example.com}{alex.johnson@example.com} \\[5pt]
    {\faLinkedin} \href{https://www.linkedin.com/in/alexjohnson}{linkedin.com/in/alexjohnson} \quad
    {\faGithub} \href{https://github.com/alexjohnsondev}{github.com/alexjohnsondev}
\end{center}

\section*{Objective}
To work as a Front-End Developer, contributing to innovative projects and expanding my skills in technology.

\vspace{0.5em}

\section*{Summary of Qualifications}
Front-End Developer with experience in JavaScript, React, Java, and Elixir. Career transition from administration to technology in 2020 through a software engineering bootcamp. Participation in relevant projects, including a Hackathon in Germany and an exchange programme in Spain.

\section*{Education}
\textbf{Computer Science} - University of Manchester | 3rd Year - Expected 2026  \\
\textbf{Diploma in International Trade} | University College London | 2018 - 2019 

\section*{Professional Experience}
\textbf{Tech Solutions Ltd.} \hfill May/2023 - Present  \\
\textbf{Front-End Developer}  \\
Developed multiple projects from conception, enhancing understanding of product impact on business. Led Front-End development for internal products, including CMS, and corporate websites for clients in the automotive sector. Also contributed to the development of an interactive landing page and a vehicle registration lookup tool. \\
\\
\textbf{Innovate Digital} \hfill April/2021 - April/2023  \\
\textbf{Front-End Developer}  \\
Worked in the Payments team, implementing improvements and developing new user flows. Led the development of a feature that enabled business account registrations, previously unavailable. Contributed actively to both Front-End and Back-End development, achieving a strategic company milestone.

\vspace{0.5em}

\section*{Additional Education}
\textbf{Cybersecurity}, Google, Coursera | Ongoing  \\
\textbf{Exchange Programme}, Spanish A2, Language Institute – Spain | 2021 \\
\textbf{Bootcamp}, Full Stack Development, Code Academy | 2020  

\section*{Languages}
\textbf{English:} Native \quad
\textbf{Spanish:} Intermediate (B2) \quad
\textbf{French:} Basic (A2)

\vspace{0.5em}

\section*{Technologies and Other Information}
\textbf{Front-End:} HTML, CSS, JavaScript, TypeScript, React, Redux, Next.js, Tailwind CSS.  \\
\textbf{Back-End:} Java, Elixir, GraphQL, .NET, C, C++.  \\
\textbf{Tools:} Git, GitHub, Docker, Grafana.  \\
\textbf{Methodologies:} Scrum, Kanban  

\end{document}
